---
title: Adding figures and other images to posts
date: '2017-10-06'
slug: adding-figures-and-other-images-to-posts
---

With **blogdown**, you can include figures that result from R code like plots as well as images from other sources in posts. For the former, you will need to be working from an R Markdown post, but for the latter, you can be working in either a markdown or R Markdown post. To read more about the differences between the two posting formats, read [this chapter](https://bookdown.org/yihui/blogdown/output-format.html) in the **blogdown** book.

# Example 1: Including figures from R code

In an R Markdown post, you can insert an R code chunk that produces a figure like this:

```{r message = FALSE, warning = FALSE}
library(ggplot2)
oplot <- ggplot(Orange, aes(x = age, 
                   y = circumference, 
                   colour = Tree)) +
  geom_point() +
  geom_line() +
  guides(colour = FALSE) +
  theme_bw()
oplot
```

You can use the **knitr** chunk options to control aspects of how the figure is displayed. Read more about these options in the [**bookdown** book](https://bookdown.org/yihui/bookdown/figures.html).

You may also use the chunk options to automatically produce numbered figures with captions. To do this, you will need to do two things:

1. Label the R code chunk used to produce the figure 
2. Use the `fig.cap =` chunk option to provide a figure caption. 

Note that the chunk label should not have underscores; it should only contain alphanumeric characters (a-z, A-Z, 0-9), slashes (/), or dashes (-). 

To reference the figure in the text of your post, use the syntax `\@ref(fig:chunk-label)`,^[Do not forget the leading backslash! And also note the parentheses `()` after `ref`; they are not curly braces `{}`.] where `chunk-label` is the label of the chunk containing the R code that produces the figure.


````markdown
`r ''````{r orange-tree-fig, fig.cap = "Growth of orange trees"}
oplot
```
````


```{r orange-tree-fig, fig.cap = "Growth of orange trees", echo = FALSE}
oplot
```

Now, a reference in the text of the post to `\@ref(fig:orange-tree-fig)` will produce a link to Figure \@ref(fig:orange-tree-fig).


