---
title: Adding GIF animations
author: Alison Presmanes Hill
date: '2018-01-31'
slug: gif-animations
categories: []
tags: []
raw: "https://raw.githubusercontent.com/rbind/blogdown-demo/master/content/post/2018-01-31-adding-gif-animations.Rmd"
---

To add a GIF animation, you need to install [FFmpeg](https://www.ffmpeg.org/download.html) on your computer. If you are on a macOS, you can install FFmpeg through [Homebrew](https://brew.sh) using the formula [`brew install ffmpeg`](http://brewformulas.org/Ffmpeg).

To make a GIF animation, use the following **knitr** chunk options:

````markdown
`r ''````{r chunk-label, fig.show='animate', ffmpeg.format='gif', dev='jpeg'}
for (i in 1:10) plot(runif(100), ylim = c(0, 1)) # for example
```
````

Which would produce the GIF below...

```{r random, fig.show='animate', ffmpeg.format='gif', dev='jpeg', echo = FALSE}
set.seed(0)
for (i in 1:10) plot(runif(100), ylim = c(0, 1))
```

Let's break those chunk options down:


* `fig.show =` `` `animate` ``: [how to show/arrange the plots](https://yihui.name/knitr/options/#plots); `animate` wraps all plots into an animation if there are mutiple plots in a chunk

* `ffmpeg.format =` `` `gif` ``: [the filename of the extension video you want to *create*](https://yihui.name/knitr/options/#animation). This `.gif` file is saved in your `/static/post/` [directory](https://github.com/rbind/blogdown-demo/tree/master/static/post/2018-01-31-adding-gif-animations_files/figure-html). 

* `dev =` `` `jpeg` ``: [the function name which will be used as a graphical device to record the individual plots that make up the above](https://yihui.name/knitr/options/#plots). These `.jpeg` files are each saved in your `/static/post/` [directory](https://github.com/rbind/blogdown-demo/tree/master/static/post/2018-01-31-adding-gif-animations_files/figure-html). 

You can also create GIFs using the [**purrr**](http://purrr.tidyverse.org) and [**ggplot2**](http://ggplot2.tidyverse.org/index.html) packages.

```{r message = FALSE, warning = FALSE}
library(purrr)
library(ggplot2)
library(repurrrsive) # for the example data below
```

Below is some sample code from an awesome [**purrr** tutorial](https://github.com/cwickham/purrr-tutorial) by [Charlotte Wickham](http://cwick.co.nz). From her `map2()` [example code](https://github.com/cwickham/purrr-tutorial/blob/master/04-map2.R):

```{r}
gap_split_small <- gap_split[1:10]
countries <- names(gap_split_small)
# For all countries
plots <- map2(gap_split_small, countries, 
  ~ ggplot(.x, aes(year, lifeExp)) + 
      geom_line() +
      labs(title = .y) +
      coord_cartesian(ylim = c(0, 100))) 
```

To show these plots as an animation, we would use this code chunk:

````markdown
`r ''````{r gapgif, fig.show='animate', ffmpeg.format='gif', dev='jpeg'}
# Display all plots
walk(plots, print)
```
````

Which produces the GIF below...

```{r gapgif, fig.show='animate', ffmpeg.format='gif', dev='jpeg', echo = FALSE}
# Display all plots
walk(plots, print)
```


